Empty Homes V1

### 2017-03-21 CreateExcelTemplates.Rmd
Cleaned up the code to prevent AG from needed to be built every time.
Added in the cornwall data and map at LSOA level.

Number of households of size x with bedrooms y
https://www.nomisweb.co.uk/census/2011/lc4405ew
```{r setup}
setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
source("Setup.R")
```

>>>>

Number of households of size x with bedrooms y
https://www.nomisweb.co.uk/census/2011/lc4405ew

```{r setup}
setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
source("Setup.R")
```

### 2017-03-21 EmptyHomesV1.Rmd
Cleaned up the code to prevent AG from needed to be built every time.
Added in the cornwall data and map at LSOA level.

@@

test <- read.xlsx("SuttonExemptionsLSOA.xlsx")
ken1 <- read.xlsx("Copy of Kensington and ChelseaCTBandsLSOA.xlsx" )
ken2 <- read.xlsx("Copy of Kensington and ChelseaExemptionsLSOA (002).xlsx")
```

@@

@@

#Padstow example
```{r}
test2 <- CTtaxstock 
pop2 <- pop %>% filter(grepl("Cornwall 008",X3))

#padstow
pad <- left_join(select(test2, ECODE, ALL_PROPERTIES), select(pop2, `Area Codes`, `All Ages`),
          by=c("ECODE" = "Area Codes")) %>% 
  mutate(diff = ALL_PROPERTIES-`All Ages`, ratio = ALL_PROPERTIES/`All Ages`) %>% filter(complete.cases(.))

@@

Bind the ward names and LAD names to the lsoa data
```{r}
setwd(PostcodeLookups)
lsoa <- read_csv("PCD11_OA11_LSOA11_MSOA11_LAD11_EW_LU_aligned_v2.csv") %>%
  select(LSOA11CD:LAD11NMW) %>% distinct(., LSOA11CD, .keep_all = TRUE)

@@

Convert shape file to dataframe and join in the LSOA data
```{r}
setwd(LSOAshapedata)

@@

@@

ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = EmptPerc), 
colour = alpha("darkred", 1/2), size = 0.7) + scale_colour_gradient2() +
  ggtitle("Lambeth coloured by areas of highest % empty Homes")

@@

AG2 <- AG2 %>% left_join(., WardDat, by = "Admin_ward_code") %>% 
  filter(Wardname != "Kensal Green")

ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = vallow), 
colour = alpha("darkred", 1/2), size = 0.7) + scale_colour_gradient2() 
```

@@

test <-read_csv("pp-2016.csv", col_names = FALSE )

#quick and dirty loses half the sales due to missing the postcode
test <- test %>% left_join(., PstCdLSOA.raw, by = c("X4"="Postcode")) %>% filter(!is.na(lsoa11cd))

test2 <- test %>% group_by(Admin_ward_code) %>% summarise( MeanPrice = mean(X2), counts =n() )

WardDat2 <- WardDat %>% left_join(., test2) %>% mutate(vallow = LowUse*MeanPrice) %>%
  filter(!is.na(MeanPrice))

@@

>>>>

#Telegraph article on pensioners requireing mortgages
http://www.telegraph.co.uk/personal-banking/mortgages/pensioner-mortgages-boom-britains-broken-housing-market/

@@

test <- read.xlsx("SuttonExemptionsLSOA.xlsx")
ken1 <- read.xlsx("Copy of Kensington and ChelseaCTBandsLSOA.xlsx" )
ken2 <- read.xlsx("NewhamExemptionsLSOA.XLSX")[,1:4]
```

@@

#VOA data

@@

@@

Bind the ward names and LAD names to the lsoa data
```{r LAD/WARD data}
setwd(PostcodeLookups)
lsoa <- read_csv("PCD11_OA11_LSOA11_MSOA11_LAD11_EW_LU_aligned_v2.csv") %>%
  select(LSOA11CD:LAD11NMW) %>% distinct(., LSOA11CD, .keep_all = TRUE)

@@

Convert shape file to dataframe and join in the LSOA data
```{r}

if(file.exists(file.path(DataFolder,"shapeframe.rds"))){
 PstCdLSOA.raw <- readRDS(file.path(DataFolder,"shapeframe.rds"))
} else{
    setwd(LSOAshapedata)

@@

    saveRDS(AG, file.path(DataFolder,"shapeframe.rds"))
    }

@@

ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = EmptPerc), 
colour = alpha("darkred", 1/2), size = 0.7) + scale_colour_gradient2() +
  ggtitle("Lambeth coloured by areas of highest % empty Homes")+
  theme(plot.title = element_text(hjust = 0.5))

@@

AG2 <-AG2 %>% left_join(., WardDat, by = "Admin_ward_code") %>% 
  filter(Wardname != "Kensal Green")%>% mutate(PercEmpt = LowUse/WardHomes)

ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = PercEmpt), 
colour = alpha("darkred", 1/2), size = 0.7) + scale_colour_gradient2() +
  ggtitle("Kensington and Chelsea low use property")+
  theme(plot.title = element_text(hjust = 0.5))

@@

prices <-read_csv("pp-2016.csv", col_names = FALSE )

#quick and dirty loses half the sales due to missing the postcode
test <- prices %>% mutate(X4 = gsub(" ", "", X4)) %>% left_join(., PstCdLSOA.raw %>% mutate(Postcode = gsub(" ", "", Postcode)), by = c("X4"="Postcode")) %>% filter(!is.na(lsoa11cd))

MeanWardPrice <- test %>% group_by(Admin_ward_code) %>% summarise( MeanPrice = mean(X2), counts =n() )

MeanWardPrice %>% ggplot(., aes(x= counts)) +geom_density()

WardDat2 <- WardDat %>% left_join(., MeanWardPrice) %>% mutate(vallow = LowUse*MeanPrice) %>%
  filter(!is.na(MeanPrice))

@@

```{r}
test <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% mutate(Empty = rowSums(.[,2:9])) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% mutate(EmptyPerc = Empty/Homes)

test2 <- test %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))

#Cornwall

setwd(file.path(RegionsComp, "Region South West"))

Cornwall <- read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
  spread(key= Exemption.type, value = counts, fill = 0) %>% 
  mutate(LowUse = rowSums(.[,c(FALSE,!grepl("exempt",(names(.)[-1])))])) %>%
  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup

Cornwall <- Cornwall %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)

Cornwall %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))  %>% 
  ggplot(.)+ 
  geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Cornwall Empty and second Homes %")+
  theme(plot.title = element_text(hjust = 0.5))

 Cornwall %>% filter(Admin_ward_code !="E05009195") %>% summarise(x =cor(MeanPrice, WardLowUsePerc, use = 'complete.obs'))

 Cornwall %>% ggplot(., aes(y=MeanPrice, x= WardLowUsePerc )) + geom_point() +
   labs(title = "Relationshibetween LowUse Percentage and Mean Price in Ward")+
  theme(plot.title = element_text(hjust = 0.5))
